\texttt{MSnbase}, efficient R-based access and manipulation of raw mass spectrometry data

### 2020-04-23 msnbase2.Rnw
add benchmarking scipts and results

Mass spectrometry is a powerful technology to assays chemical and
biological samples. It is used routinely, with well characterised
protocol, as well a development platform, to improve on existing
methods and devise new ones to analyse ever more complex sample in
greater details. The complexity and diversity of mass spectrometry
yields data that is itself complex and often times of considerable
size, that requires non trivial processing before producing
interpretable results. This is particularly relevant, and can
constitue a significant challenge for method developers that, in
addition to the development of sample processing and mass spectrometry
methods, need to process and analyse these new data to demonstrate the
improvement in their technical and analytical work.

@@

In this software note, we present version 2 of the \texttt{MSnbase}
\cite{Gatto:2012} R/Bioconductor software package. \texttt{MSnbase}
offers a platform that lies between low level libraries and end-use
software. It provides a flexible command line environment for
metabolomics and proteomics mass spectrometry-based application, that
allows a detailed step-by-step processing, analysis and exploration of
the data and development of novel computational mass spectrometry
methods.

@@

We are going to present the new raw data infrastructure that has been
available since \texttt{MSnbase} version 2.0, and then describe how it
is leveraged to process large amount of data. We are then going to
demonstrate some visualisation that make use of the raw data
structures available in \texttt{MSnbase} and conlude with an example
if flexible prototyping, by showing how to quickly combine spectra
acquired using the Boxcar method (REF).

>>>>

Mass spectrometry is a powerful technology to assay chemical and
biological samples. It is used routinely, with well characterised
protocols, as well a development platform, to improve on existing
methods and devise new ones to analyse ever more complex sample in
greater details. The complexity and diversity of mass spectrometry
yields data that is itself complex and often times of considerable
size, requiring non trivial processing before producing interpretable
results. This is particularly relevant, and can constitue a
significant challenge for method developers that, in addition to the
development of sample processing and mass spectrometry methods, need
to process and analyse these new data to demonstrate the improvement
in their technical and analytical work.

@@

In this software note, we present version 2 of the \texttt{MSnbase}
\cite{Gatto:2012} R/Bioconductor software package. \texttt{MSnbase}
offers a platform that lies between low level libraries and end-use
software. It provides a flexible and interactive command line
environment for metabolomics and proteomics mass spectrometry-based
application. It allows a detailed step-by-step processing, analysis
and exploration of the data and development of novel computational
mass spectrometry methods.

@@

We are going to present the new raw data infrastructure that has been
available since \texttt{MSnbase} version 2.0, and then describe how it
is leveraged to process large amount of data. We are then going to
demonstrate some visualisation that make use of the raw data
structures available in \texttt{MSnbase} and conlude with an example
if flexible prototyping, by showing how to quickly combine spectra
acquired using the Boxcar method \cite{Meier:2018}.
